Supplemental Materials for ``Universals of word order reflect optimization of grammars for efficient communication''

### 2019-10-25 writeup/pnas-word-order-si.tex
cleaning

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../results/plane/unlexicalized/pareto-plane-perLanguage-lexicalized-mle.pdf}
	\caption[Predictability and Parseability]{Study 1, replication with lexicalized models: Predictability and parseability of 51 languages, for \emph{lexicalized} models, compare Figure~\ref{fig:pareto-per-lang}.}\label{fig:pareto-plane-noPOS}
\end{figure}

\begin{table}
\centering
\small{
\begin{tabular}{l||ll|lll|lll}
Language & Pred. (t) & Parse. (t) & \multicolumn{3}{c|}{Pred. (Binomial)} & \multicolumn{3}{c}{Parseab. (Binomial)} \\ 
&  $p$ & $p$ &  Est. &CI & $p$ & Est. & CI & $p$  \\ \hline \hline
\input{../results/plane/unlexicalized/per-language-statistics-unlexicalized-ground.tex}
\end{tabular}
}
	\caption{Study 1, replication with lexicalized models: Per-language results in Study 1, with \emph{lexicalized} parsers and word-level-only language models. Compare Table~\ref{fig:pareto-per-lang-stats}}\label{tab:pareto-plane-noPOS}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../results/plane/unlexicalized/analyze_pareto_optimality/figures/quantileByLambda-mle.pdf}
	\caption{Study 1, replication with lexicalized models: Optimality of real grammars for efficiency, compared to baselines, across values of $\lambda$: The $x$-axis shows $\lambda \in [0,1)$, the $y$-axis shows the fraction of baselines that have lower efficiency than the real grammar at this value of $\lambda$, with 95\% confidence bands obtained from a two-sided binomial test. Compare Figure~\ref{fig:lambda-quantile}.}\label{fig:lambda-quantile-noPOS}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../results/plane/pureUD/analyze_pareto_optimality/figures/quantileByLambda-mle.pdf}
	\caption{Study 1, replication with the original UD format: Optimality of real grammars for efficiency, compared to baselines, across values of $\lambda$: The $x$-axis shows $\lambda \in [0,1)$, the $y$-axis shows the fraction of baselines that have lower efficiency than the real grammar at this value of $\lambda$, with 95\% confidence bands obtained from a two-sided binomial test. Compare Figure~\ref{fig:lambda-quantile}.}\label{fig:lambda-quantile-pureUD}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../results/plane/unlexicalized/pareto-plane-perLanguage-lexicalized.pdf}
	\caption[Predictability and Parseability]{Study 1, replication with lexicalized models: Predictability and parseability of 51 languages, for \emph{lexicalized} models, compare Figure~\ref{fig:pareto-per-lang}.}\label{fig:pareto-plane-noPOS}
\end{figure}

\begin{table}
\centering
\small{
\begin{tabular}{l||ll|lll|lll}
Language & Pred. (t) & Parse. (t) & \multicolumn{3}{c|}{Pred. (Binomial)} & \multicolumn{3}{c}{Parseab. (Binomial)} \\ 
&  $p$ & $p$ &  Est. &CI & $p$ & Est. & CI & $p$  \\ \hline \hline
\input{../results/plane/unlexicalized/per-language-statistics-lexicalized.tex}
\end{tabular}
}
	\caption{Study 1, replication with lexicalized models: Per-language results in Study 1, with \emph{lexicalized} parsers and word-level-only language models. Compare Table~\ref{fig:pareto-per-lang-stats}}\label{tab:pareto-plane-noPOS}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../results/plane/unlexicalized/analyze_pareto_optimality/figures/quantileByLambda.pdf}
	\caption{Study 1, replication with lexicalized models: Optimality of real grammars for efficiency, compared to baselines, across values of $\lambda$: The $x$-axis shows $\lambda \in [0,1)$, the $y$-axis shows the fraction of baselines that have lower efficiency than the real grammar at this value of $\lambda$, with 95\% confidence bands obtained from a two-sided binomial test. Compare Figure~\ref{fig:lambda-quantile}.}\label{fig:lambda-quantile-noPOS}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../results/plane/pureUD/analyze_pareto_optimality/figures/quantileByLambda.pdf}
	\caption{Study 1, replication with the original UD format: Optimality of real grammars for efficiency, compared to baselines, across values of $\lambda$: The $x$-axis shows $\lambda \in [0,1)$, the $y$-axis shows the fraction of baselines that have lower efficiency than the real grammar at this value of $\lambda$, with 95\% confidence bands obtained from a two-sided binomial test. Compare Figure~\ref{fig:lambda-quantile}.}\label{fig:lambda-quantile-pureUD}
\end{figure}
